---
title: "categorization online pilot"
output: html_notebook
---
#five partiicpants (they are in the pilot) - were directed into another qualtrics survey( probably the amplification stuff. )

#upload all csv files
```{r preparing the dataset, include=FALSE,echo=FALSE}
rm(list = ls())

library(Rmisc);library(tidyverse); library(lme4); library(lmerTest); 
library(jsonlite)

d <-
    list.files(pattern="*.json") %>% #get a list of all  files
    map_df(~fromJSON(file.path(.),
              simplifyVector = TRUE, 
              flatten = T)) #add these files to d

d=as.data.frame(d)
d=subset(d, singleStim != "NA")


d= d %>%
  filter(singleStim!="NA") %>% #remove all non-relevant files
  select(rt,
         groupChoice=button_pressed,
         trialOld=trial_index,
         time_elapsed,
         id=participant_id,
         fixationTime,
         faceIdentity,
         photo=singleStim,
         rating,
         ratingTime,
         sampleSD,
         sampleMean,
         starts_with("pos"),
         meanAgents,
         photoDescription =description)%>%
  group_by(id)%>%
  mutate(trial=seq(from =-3, to =20))%>%
  filter(trial>0)%>%
  ungroup()%>%
  separate(photo,into = c("file","photo"),sep = -7)%>%
  separate(photo,into = c("photo", "fileEnding"), sep = "\\.")%>%
  select(-file,-fileEnding)

d$photo = as.integer(d$photo)
d$rating=as.integer(d$rating)
d$groupChoice=as.integer(d$groupChoice)

#define varialble
d$condition = ifelse(d$rating==d$sampleMean,"same",
                     ifelse(d$rating>d$sampleMean,"low",
                            "high"))
d$groupChoice=ifelse(d$groupChoice==0,1,0)
d$condition=factor(d$condition)
d$condition1 = d$condition#create a copy of condition
contrasts(d$condition1) = cbind (same = c(2,-1,-1) , dif = c(0, 1,-1))
d$condition_bi = ifelse(d$condition == "same", 1,2)
d$condition_bi = factor (d$condition_bi, label =c("Same Mean", "Different Mean"))
#d=subset(d,citizen ==1)
d$condition_biEffect= ifelse(d$condition_bi=="Same Mean",-1,1)


#combind moderator file
#m = read_csv('belonging_moderators.csv') # we are reading the moderators file (which was collected via qualtrics)
#m = m[,c(19:93)] #cleaning
#d = left_join(d,m, by="id") #combining the two datasets based on participants' id


#create scales and define vairables in the new extended file
#d$identscale = (rowMeans(d[,c('iden1', 'iden2', 'iden3', 'iden4','iden5' )], na.rm=T)) #create a group identicia
#d$identscale=d$identscale-13
#d$sex = if_else(d$sex==2, "male", "female") # transform group choise into 0 or 1

dfc <- summarySE(d, measurevar="groupChoice", groupvars=c("condition_bi", "sampleSD"), na.rm = T)
dfc$sampleSD=factor(dfc$sampleSD)

pd <- position_dodge(.1)


g=ggplot(dfc,aes(x=condition_bi, y=groupChoice ,fill = sampleSD ))+
  geom_bar(position=position_dodge(), width = 0.5,stat="identity", colour="black" )+
  geom_errorbar(aes(ymin=groupChoice-ci, ymax=groupChoice+ci), width=.1,position=position_dodge(.5))+
  theme_bw()+
  theme(plot.title = element_text(size = rel(1.4), hjust = 0.5,),
        axis.title.y = element_text(face="bold",  size=14),
        axis.text.x  = element_text( vjust=0.5, size=18),
        axis.text.y  = element_text( vjust=0.5, size=12),
        axis.title.x = element_blank()) +
    scale_fill_grey()+
   coord_cartesian(ylim=c(0, 1)) +
  geom_hline(yintercept = 0.5,linetype="dashed", color = "red")+
    labs(title = "Probability of Self-Categorization based on Group Mean and SD", x = "",y = "P(self-categorization)");g


```

#get texts to filter participants

```{r}


texts = d %>%
  select(id,photo, photoDescription,trial)%>%
  filter(trial %in% c(1,6,11,16,21,26,31,36,41,46))

```


#descriptives
```{r}

addmargins(table(d$condition)) # how many people we have in each condition 
length(unique(d$id)) # get the amount of unique ids 

des= d %>%
  group_by(id)%>%
  slice(1)

race =des %>%
  select(white, black, asian,latin,other)%>%
  gather (race, value, -id) %>%
  group_by(race) %>%
  count (value==1)

mean(des$age)
sd (des$age)

table(des$sex)



```


#main analysis

###question 1 - difference in choice

Do we have a difference in choice based on condition? we compraed the same to the low and the high conditions. I think we should also consider to do orthogonal comparison here comparing the same to both and then low to high
```{r similar vs. different}
#groupChoice; 0 - not my group , 1 - my group
r = glmer(groupChoice~condition_bi +(1|id), family = binomial, d);summary(r)


#confidence interval
confint(r,level = .95)

#effect size (using the package r2glmm)

library (MuMIn)
r.squaredGLMM(r)



#grpah 
dfc <- summarySE(dd, measurevar="groupChoice", groupvars=c("condition_bi"), na.rm = T)
pd <- position_dodge(.1)
g=ggplot(dfc,aes(x=condition_bi, y=groupChoice , fill = "Black" ))+
  geom_bar(position=position_dodge(), width = 0.5,stat="identity", colour="black" )+
  geom_errorbar(aes(ymin=groupChoice-ci, ymax=groupChoice+ci), width=.1,position=position_dodge(.9))+
  theme_bw()+
  theme(plot.title = element_text(size = rel(1.5), hjust = 0.5),
        legend.position = "none",
        axis.title.y = element_text(face="bold",  size=14),
        axis.text.x  = element_text( vjust=0.5, size=18),
        axis.text.y  = element_text( vjust=0.5, size=12),
        axis.title.x = element_blank()) +
    scale_fill_grey()+
   coord_cartesian(ylim=c(0, 1)) +
  geom_hline(yintercept = 0.5,linetype="dashed", color = "red")+
    labs(title = "Probability of Self-Categorization based on Group Mean", x = "",y = "P(self-categorization)");g

```


```{r sd manipulation}
r = glmer(groupChoice~sampleSD*condition_bi +(1|id),family= binomial, d);summary(r)


#confidence interval
#confint(r,level = .95)

r.squaredGLMM(r)



dfc <- summarySE(d, measurevar="groupChoice", groupvars=c("condition_bi", "sampleSD", "id"), na.rm = T)
dfc$sampleSD=factor(dfc$sampleSD)

pd <- position_dodge(.1)
g=ggplot(dfc,aes(x=condition_bi, y=groupChoice ,fill = sampleSD ))+
  geom_bar(position=position_dodge(), width = 0.5,stat="identity", colour="black" )+
  geom_errorbar(aes(ymin=groupChoice-ci, ymax=groupChoice+ci), width=.1,position=position_dodge(.5))+
  theme_bw()+
  theme(plot.title = element_text(size = rel(1.4), hjust = 0.5,),
        axis.title.y = element_text(face="bold",  size=14),
        axis.text.x  = element_text( vjust=0.5, size=18),
        axis.text.y  = element_text( vjust=0.5, size=12),
        axis.title.x = element_blank()) +
    scale_fill_grey()+
  facet_wrap(~id)+
   coord_cartesian(ylim=c(0, 1)) +
  geom_hline(yintercept = 0.5,linetype="dashed", color = "red")+
    labs(title = "Probability of Self-Categorization based on Group Mean and SD", x = "",y = "P(self-categorization)");g

ggsave(g,  device = "pdf")

ggsave("mtcars.pdf")
```


##suplemenraty materials 

```{r similar vs. differennt -higher vers lower}


r = glmer(groupChoice~condition1+(1|id), family = binomial, d);summary(r)

confint(r,level =.95)

dfc <- summarySE(d, measurevar="groupChoice", groupvars=c("condition"), na.rm = T)
dfc$condition = c("Similar", "Lower","Higher")

pd <- position_dodge(.1)
g=ggplot(dfc,aes(x=condition, y=groupChoice , fill = "Black" ))+
  geom_bar(position=position_dodge(), width = 0.5,stat="identity", colour="black" )+
  geom_errorbar(aes(ymin=groupChoice-ci, ymax=groupChoice+ci), width=.1,position=position_dodge(.9))+
  theme_bw()+
  theme(plot.title = element_text(size = rel(1.5), hjust = 0.5),
        legend.position = "none",
        axis.title.y = element_text(face="bold",  size=14),
        axis.text.x  = element_text( vjust=0.5, size=18),
        axis.text.y  = element_text( vjust=0.5, size=12),
        axis.title.x = element_blank()) +
    scale_fill_grey()+
   coord_cartesian(ylim=c(0, 1)) +
  geom_hline(yintercept = 0.5,linetype="dashed", color = "red")+
    labs(title = "Probability of Self-Categorization based on Group Mean", x = "",y = "P(self-categorization)");g



```




####question 2 - difference in choice based on participant's initial rating? 
```{r}
r = glmer(groupChoice~rating +(1|id), family=binomial, d);summary(r)


r = lm(identscale~rating , d);summary(r)

```


####question 3- potential moderators.


```{r gender}

confint(r, level = .95)


r = glmer(groupChoice~sex+(1|id),family=binomial, d);summary(r) #identity scale does not predict rate

confint(r, level = .95)


```

```{r race}

d$race = ifelse(d$white==1, 1, 0)


r = glmer(groupChoice~race(1|id),family = binomial, d);summary(r) #identity scale does not predict rate
confint(r, level = .95)

```



```{r political affiliation1}

r = glmer(groupChoice~scale(poli) +(1|id),family=binomial, d);summary(r) #identity scale does not predict rate

confint(r,level = .95)
```


```{r idencitfication}

iden = d%>%
  group_by(id)%>%
  slice(1)%>%
  ungroup()%>%
  select(starts_with("iden"), -identscale)

psych::alpha(iden)

d$identscale = (rowMeans(d[,c('iden1', 'iden2', 'iden3', 'iden4','iden5' )], na.rm=T)) #create a group identicia



r = glmer(groupChoice~scale(identscale) +(1|id),family=binomial, d);summary(r) #identity scale does not predict rate

confint (r, level=.95)
```


```{r political affiliation}

r = glmer(groupChoice~scale(poli) +(1|id),family=binomial, d);summary(r) #identity scale does not predict rate

confint(r,level = .95)
```



####question 5 - accuracy in the same condition as precitrr of the other conditions**

```{r}

g = d%>%
  subset (condition != "same") %>%
    ggplot(.,aes(x=sameAccuracy, y=groupChoice)) +
    geom_point() +
    facet_wrap(~condition)+
    stat_smooth(method="glm", method.args=list(family="binomial"))
g
```





####power analysis of initial sample  
```{r}

library (simr)

p=subset(d, id<13)

p$condition_bi=as.integer(p$condition_bi)


r = glmer(groupChoice~condition_bi +(1|id), family = binomial,p);summary(r)

power =powerSim(r,fixed("condition_bi"),nsim=100)

model1 = extend(r,along="id", n=30)

pc = powerCurve(model1, along = "id",nsim =100)
 pl

port
fixef(r)


```
###distributions of the group 

```{r}
dis = read_csv("face_distribution_calculation10sd.csv")


dis%>%
  gather%>%
  ggplot(data=., aes(value))+ 
    geom_histogram()+
    facet_wrap(~key)


```



#### model - generate files

We first need to transform each participants into a list of lists. 

```{r generate json files -only use once}

library(jsonlite)


files = d%>%
  select (id, starts_with("par"), -partUSText, -partUS ,trial,rating) %>%
  group_by(id)%>%
  gather (par, agentRating,-trial,-id)  %>%
  spread(trial, agentRating)%>%
  select( -par)

list_id = unique(files$id)
  
for (i in list_id){
  print (i)
  df = subset (files,id ==i)
  df$id = NULL
  df = as.list(df)
  df =toJSON(df, pretty = TRUE)
  write(df, sprintf('C:/Users/chaga/Google Drive/research/categorization_belonging/categorization_manipulating_mean/model/json_files/id_%d.json', i))
}


```



#check R^2

```{r}

d$test = ifelse(d$condition_bi=="Same Mean", 1,0)

d$test[1:4] = c(1,1,0,0)


r= glmer (test ~ condition + (1|id), family = binomial,d); summary(r)



r2beta(model = r, method = 'sgv', data = d)

```

